---
title: "Airbnb_Shiny"
output: html_notebook
---

Load libraries
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(leaflet)
library(leaflet.extras)
```

Set working directory and load the data
```{r}
setwd('~/desktop/nyc-airbnb')
raw = read.csv('AB_NYC_2019.csv',stringsAsFactors = F)
```

Step 0: Basic analysis
```{r}
names(raw)
head(raw)
unique(raw$neighbourhood_group)
raw %>% group_by(neighbourhood) %>% summarise( count = n() ) #217 unique neighbourhood

# Is it reasonable to filter out locations that shared their room once?
raw %>% group_by(host_id) %>% summarise(count = n()) %>% filter(count == 1) %>% dim()
# No, there are 32,303 unique host_id that shared their room once

# Is it reasonable to filter out reviews <= 0
raw %>% filter(number_of_reviews <= 0) %>% dim()
# 10,052 rows, Not sure at the moment
# Why would we want to keep this information? 
```
Step 0: Cleaning/Formating
```{r}
#Change neighborhood_group to boro
raw = raw %>% rename( boro = neighbourhood_group)

#Identify availability_365 = 0 and # reviews = 0
no_business = raw %>% filter(availability_365 == 0, number_of_reviews == 0)
#4,845 rows of no business
raw = raw %>% filter(availability_365!=0, number_of_reviews!=0)
# Does the reasons provide good rationale to justify that they provide no business?  Yes.


# Add price room per night column
raw = raw %>% mutate( price_night = price/minimum_nights )

#Active locations? We are going to define active locations as a location with last review date was in 2019
#convert to datetime format
raw$last_review = as.Date(raw$last_review, '%Y-%m-%d')
raw = raw %>% mutate(recent_year = as.numeric(year(last_review)))
# count of year of review entries
count_year = raw %>% group_by(recent_year) %>% summarise( count = n() )

#Save as new file
#write.csv(raw,'airbnb_nyc.csv')
```

Step 2: Analysis

1. Relationship between price of location and boro.
Appoarch: x = boro y1 = mean price y2 = median, proportion of prices between each boro
```{r}
# Average and median price for each boro
boro_prices= raw %>% group_by(boro) %>%  summarise(Average=mean(price), Median=median(price))

# Shiny bar plot Basic analysis: price comparisons of each boro 
ggplot(boro_prices, aes(x=boro, y= Median ) )+ 
  geom_bar(stat = 'identity', aes(fill = boro) ) +
  ggtitle('Comparison between Price and Location') +
  xlab('')+ theme(legend.title = element_blank(),
                  legend.position = "none",
                  plot.title = element_text(hjust = 0.5, size = 14))

# Shiny density plot idea: make the graph interactive by having a zoom in
ggplot(raw, aes(x=price) )+  geom_density(aes(color = boro) )+  
  labs(color = "Location")+
  xlim(0,250)


### Same concept but using price_night###

# Average and median price/night for each boro
boro_prices_n = raw %>% group_by(boro) %>%  summarise(Average=mean(price_night), Median=median(price_night))
# transpose the data
# boro_prices_n = as.data.frame(t(as.matrix(boro_prices_n)))


# Shiny bar plot Basic analysis: price/night comparisons of each boro 
ggplot(boro_prices_n, aes(x= boro ) )+ 
  geom_bar(stat = 'identity',aes(y = Median, fill = boro) ) +
  ggtitle('Comparison between Price/night and Location') +
  xlab('')+ theme(legend.title = element_blank(),
                  legend.position = "none",
                  plot.title = element_text(hjust = 0.5, size = 14))

# Shiny density plot idea: make the graph interactive by having a zoom in
ggplot(raw, aes(x=price_night) )+  geom_density(aes(color = boro) )+  
  labs(color = "Location")+
  xlim(0,250)
```

2. Relationship between price for each neighborhood. 

```{r}
# Average and median price/night of each neighbourhood
neighbour_price_n = raw %>% group_by(neighbourhood, boro) %>% summarise(Average = mean(price_night), Median = median(price_night) )

# What does this show???
ggplot(neighbour_price_n, aes(x= Average, y= Median) ) + geom_point(aes(color = boro)) + xlim(0, 150) + ylim(0, 150)

#Average price and price/night of each neighborhood
neighbour_price_com = raw %>% select(boro, neighbourhood, price, price_night) %>% group_by( neighbourhood, boro) %>% summarise( avg_price = mean(price), avg_price_n = mean(price_night) )

### Relationship between avg price and avg price/night for each boro ###
# Plot the avg price, avg price/night of each neighboorhood then 
ggplot(neighbour_price_com, aes(x= avg_price, y=avg_price_n)) +
  geom_point(aes(color = boro) )+ 
  #geom_smooth(aes( color=boro), se=F)+
  xlab('Average Price')+ ylab('Average Price/night')+
  xlim(25, 200) + ylim(0, 150)
```

What did we get when comparing average price and average? 

3. Relationship of each boro based price with time
```{r}
#No set start/end time
ggplot(raw, aes(x=last_review, y= price_night))+geom_smooth(aes( color= boro), se=F)
# Looking at the raw data, there a signficantly lower amount of last_review during earlier years.

#Only 2018-2019
recent_data = raw %>% filter((year(last_review) == 2019) | (year(last_review) == 2018))
ggplot(recent_data, aes(x=last_review, y=price_night))+geom_smooth(aes(color = boro), se=F )

#Only 2019 because largest amount of volume
recent_data = raw %>% filter(year(last_review)==2019)
ggplot(recent_data, aes(x=last_review, y=price_night) )+geom_smooth(aes(color=boro),se=F)
```

4.Relationship of price/night with recent time for each neighborhood in each boro

```{r}
#Manhattan
boro_data = recent_data %>% filter(boro=='Manhattan') %>%
  select(boro, price, price_night, neighbourhood, last_review) %>% group_by(neighbourhood) %>% 
  top_n(neighbourhood,n= 5)
ggplot(boro_data, aes(x=last_review, y=price_night))+geom_point(aes(color=neighbourhood), se=F)
```


5. Heatmap based on price? Display a visual that displays locations with desired price range

```{r}
raw %>% 
  group_by(latitude, longitude) %>% summarise( n())
  leaflet() %>% addTiles() %>% 
  addHeatmap(lng = ~longitude, lat = ~latitude, radius = 8)

```


6. How does avialability affect price? Is there a relationship between price and avialbility?
sample = our data

```{r}
cor_pn_365=raw %>% select(price_night, availability_365) %>% cor()
cor_raw = raw %>% select(price,price_night,minimum_nights,reviews_per_month,availability_365) %>% cor()
library(corrplot)
library(RColorBrewer)

corrplot(cor_pn_365,type="upper", order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))

corrplot(cor_raw, method = 'pie',type = 'lower', order = 'hclust', 
         col=brewer.pal(n=8, name="RdYlBu"))

```



